### 2019-08-02 thesis.tex
*** empty log message ***

The analysis presented in this doctoral thesis has relevant contributions in the
study of the combined action of nonlinear kinetic instabilities and collisional
processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
profile under consideration might be considered quite idealized, the physical
processes that are being addressed have fundamental character - the plasma waves
under consideration and the particle interactions are inherent to any plasma.
The underlying nature of these processes means that they might impact the plasma
dynamics at different astrophysical environments and also in laboratory plasmas.
Laboratory plasmas, however, are usually constrained by very specific conditions
that are unique to each experiment. This specificity makes the analysis in the
experimental context counter productive. A more broad approach was then to compare
our theoretical results with phenomena observed in the naturally occurring space
plasma\footnote{In the literature, the term ``astrophysical plasma'' is sometimes
  used to refer to the plasma observed outside the solar system, while ``space
  plasma'' is used to account for the plasma in our interplanetary space. In this
  text, however, both terms are being used as synonyms.}.

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\footnote{For a relatively
  brief, but comprehensive, description of the scales and characteristics of
  cosmic plasmas, see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the
outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
the observable matter in the universe is in the plasma state\cite{may}. Under
cosmic conditions, even the weakly ionized gas of the neutral hydrogen regions
around galaxies or in the atmosphere of cold stars have a strong reaction to
electromagnetic fields, exhibiting the characteristic collective behavior of
plasmas\cite{tsypa,peratt2014}.

Due to the pervasiveness of the plasma state in space, plasma physics became
an essential component in the multidisciplinary framework of astrophysics.
At the same time, observations of space plasma phenomena have been gaining
increasing relevance in theoretical, computational, and experimental areas
of plasma physics research \cite{Kulsrud2005}. This mutual contribution is
driven by solar physics.

>>>>

The analysis presented in this doctoral thesis has relevant contributions in the
study of the combined action of nonlinear kinetic instabilities and collisional
processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
profile under consideration might be considered quite idealized, the physical
processes that are being addressed have fundamental character - the plasma waves
under consideration and the particle interactions are inherent to any plasma.
The underlying nature of these processes means that they might impact the plasma
dynamics at different astrophysical environments and also in laboratory plasmas.
Laboratory plasmas, however, are usually constrained by specific experimental
set-up. This specificity would require deep knowledge, and maybe access, to one
experiment, which makes the analysis in the experimental context restrictive and
counter productive. A more broad approach was then to compare our theoretical
results with phenomena observed in the naturally occurring space plasma.

% \footnote{In the literature, the term ``astrophysical plasma'' is sometimes used
%   to refer to the plasma observed outside the solar system, while ``space plasma''
%   is used to account for the plasma in our interplanetary space. In this text,
%   however, both terms are being used as synonyms.}

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\footnote{A comprehensive
  description of the scales and characteristics of cosmic plasmas can be seen
  in Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the outer layers of
Earth's atmosphere, passing through the solar wind in the interplanetary space,
to the stellar interiors and atmospheres, accretion disks, and molecular clouds
it is estimated that something around $99 \sim 99.9\%$ of the observable matter
in the universe is in the plasma state. Under cosmic conditions, even the weakly
ionized gas of the neutral hydrogen regions around galaxies or in the atmosphere
of cold stars have a strong reaction to electromagnetic fields, exhibiting the
characteristic collective behavior of plasmas and, therefore, are also considered
plasmas\cite{tsypa,may,peratt2014}.

Since the pervasiveness of the plasma state in space came as a fact, plasma
physics became an essential component in the multidisciplinary framework of
astrophysics. At the same time, observations of space plasma phenomena have
been gaining increasing relevance in the advance of theoretical, computational,
and experimental plasma physics research \cite{Kulsrud2005}. This mutual contribution is
driven by solar physics.
